### 2019-06-28 thesis.tex
New version of section 1

\section{Astrophysical plasmas}
\label{sec:astro-plasma}
On Earth, the plasma is considered an exotic state of matter, associated to the
glowing gas inside fluorescent and neon lamps, microchip manufacturing, research
laboratories, and the promise of cleaner and technically infinite energy source
when scientists and engineers manage to succeed at obtaining a controlled, and
energetically efficient, thermonuclear fusion. Naturally occurring plasmas in our
everyday life are rare, restricted to the occurrence of lightning during storms
and beautiful auroras that are spotted at high latitudes. In the interplanetary
and interstellar space, however, the situation is the opposite. Starting in the
outer layers of Earth's atmosphere, passing through the solar wind in the
interplanetary space, to the stellar interiors and atmospheres, accretion disks,
and molecular clouds it is estimated that something around $99 \sim 99.9\%$ of
the observable matter is in the plasma state \cite{may}.

% Astrophysics is a millennial observational science, that started with bare eyes
% observation of the sky, describing the constellations, and solar, lunar and
% planetary cycles. These first observations of the relative motion of planetary
% bodies led to solar clocks, calendars, and navigation charts. Nowadays, we have
% extremely sophisticated equipment of observation, both on Earth and in space,
% that can reach

>>>>

\section{Kinetic processes in astrophysical plasmas}
\label{sec:astro-plasma}
The plasma, as a collection of ions and electrons, has its dynamics
dominated by the electric and magnetic fields generated by the presence
of charged particles, and electric currents that arise from their
movement. Due to the long-range nature of these self-generated fields,
one particle affects the movement of several other particles, which
will interact with other particles, and so on. This \emph{collective
  behavior}\footnote{A more detailed description on all the processes
  and conditions that characterize the collective behavior in neutral
  plasmas can be seen in Refs. \cite{bitt,gurnett2017,chen}. For
  nonneutral plasmas, see Ref. \cite{DavidsonNonNeutral}.} is what
characterizes an ionized gas as a plasma, and also is the reason behind
the complexity of the plasma dynamics.
